Introducing Distributed Dynamic Data-intensive (D3) Science: Understanding Applications and Infrastructure

### 2016-02-22 3dpas_intro.tex
addressing DSK's comments.

The landscape of scientific and enterprise computing is being fundamentally
altered by prodigious volumes of data.  Occasionally data are often
naturally distributed and have to be processed near their source, and sometimes data that
are localized have to be distributed in order to be processed, either for
reasons of performance or for collaborative analytics. Further, the scale of
varying data source and destination, as well as the transfer of production rates \katznote{what are `transfer of production rates'?}
makes temporal variations in data properties increasingly important.  With an
increase in the importance of distributed and temporal properties of data,
systems and infrastructure aspects such as resource scheduling, data placement,
and transfer decisions that were statically determinable at small scales emerge
as dynamic and important considerations at large scales of data and
distribution.

@@

Nowadays, NGS sequencers are even being shipped with servers or small
clusters for performing the alignment and re-sequencing as a pipeline
right after the reads have been generated~\cite{ilm}.
%\alnote{What kind of codes are used
%in these clusters? What are the characteristics of these codes?}
%But any additional analysis is not supported.
%\alnote{What would be an additional analysis}
%
Scientific workflow systems like Taverna~\cite{Taverna:2006}, BioKepler~\cite{biokepler:2011}, and
Galaxy~\cite{galaxy} (though Galaxy does not support distributed systems currently) have been successful in integrating genome
analysis tools for bioinformatics. Script-based pipelines that combine
executables are also often used. Very few workflow systems have
explicit support for distributed data or dynamic data handling.
Therefore reusable approaches at extending existing tools to support
distributed and dynamic data are likely to be useful.
%\katznote{Shantenu/Yogesh/Andre, please read this paragraph and tell me if changes
%should be made to this section at this point}\alnote{ok with me}

>>>>

The landscape of scientific and enterprise computing is being fundamentally
altered by prodigious volumes of data.  Occasionally data are often naturally
distributed and have to be processed near their source, and sometimes data that
are localized have to be distributed in order to be processed, either for
reasons of performance or for collaborative analytics.  Further, the variation
of data production rates, data source and destination makes temporal variations
in data properties increasingly important.  With an increase in the importance
of distributed and temporal properties of data, systems and infrastructure
aspects such as resource scheduling, data placement, and transfer decisions that
were statically determinable at small scales emerge as dynamic and important
considerations at large scales of data and distribution.

@@

%\alnote{What kind of codes are used
%in these clusters? What are the characteristics of these codes?}
%But any additional analysis is not supported.
%\alnote{What would be an additional analysis}
%

NGS sequencers such Illumina and Ion Torrent provide the option of onsite
servers or small clusters for performing the alignment and re-sequencing as a
pipeline right after the reads have been generated.  Scientific workflow systems
like Taverna~\cite{Taverna:2006}, BioKepler~\cite{biokepler:2011}, and
Galaxy~\cite{galaxy} (though Galaxy does not support distributed systems
currently) have been successful in integrating genome analysis tools for
bioinformatics. Script-based pipelines that combine executables are also often
used. Very few workflow systems have explicit support for distributed data or
dynamic data handling.  Therefore reusable approaches at extending existing
tools to support distributed and dynamic data are likely to be useful.
%\katznote{Shantenu/Yogesh/Andre, please read this paragraph and tell me if changes
%should be made to this section at this point}\alnote{ok with me}
